---
title: {{{ Title }}}
author: {{{ Author }}}
date: {{{ Date }}}
format:
  html:
    toc: true
    number-sections: true
    embed-resources: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Background

*Add a brief background to the study*

# Research Questions

*Include the study research questions*


# Objectives

*Add the study objectives, delete section that are unused*

## Primary Objectives

## Secondary Objectives

## Exploratory Objectives


# Data Sources

<!-- Add data sources -->

*Example table for data sources*

```{r}
#| label: tbl-data_sources
#| echo: false
#| tbl-cap: Data Sources used in study

dataSources <- tibble::tribble(
  ~Name, ~Country, ~Type, ~Size, ~Availability, ~Description,
  "Synpuf", "US", "claims", "110K", "2008-2010", "Synthetic data source based on US Medicare data"
)

flextable::flextable(dataSources)

```

# Cohorts

*Provide information on the cohorts used in the analysis*

## Target

## Exposures

## Outcomes

## Diagnostics


# Analysis Plan

*Provide information on how the analysis will be done*

## Stratafication

## Covariates

*Example of covariate table*

```{r}
#| label: tbl-cov
#| tbl-cap: Covariates used for study

cov <- tibble::tribble(
  ~`Domain`, ~`Covariate`, ~`Time`, ~`Stat`,
  "Demographics", "age 5yr", "at index", "count (%)",
  "Demographics", "age continuous", "at index", "median (25th-75th)",
  "Demographics", "gender", "at index", "count (%)",
  "Demographics", "healthcare plan", "at index", "count (%)",
  "Demographics", "time in cohort", "at index", "median (25th-75th)",
  "Conditions", "Diabetes Mellitus", "365d prior", "count (%)",
  "Conditions", "Hypertension", "365d prior", "count (%)",
  "Conditions", "Heart Failure", "365d prior", "count (%)",
  "Conditions", "Systolic Heart Failure", "365d prior", "count (%)",
  "Conditions", "Diastolic Heart Failure", "365d prior", "count (%)",
  "Conditions", "Chronic Kidney Disease", "365d prior", "count (%)",
  "Conditions", "Myocardial Infarction", "365d prior", "count (%)",
  "Conditions", "Stroke", "365d prior", "count (%)",
  "Conditions", "ICD10 Chapters", "365d prior", "count (%)",
  "Drugs", "ATC2", "365d prior", "count (%)",
  "Drugs", "Anticoagulants", "365d prior", "count (%)",
)

flextable::flextable(cov)
```


## Outcome Definitions

## Data Analysis


